---
title: "GSS challange"
author: "Zaira Gomez"
date: "October 14 ,2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)?

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->


```{r}
barchartGC(~POSTLIFE + BIGBANG,data=GSS)
barchartGC(~POSTLIFE + BIGBANG,data=GSS, type="percent")

```

Looking at this graph it appears there is a lot more people who believe in postlife and the majority of these people believe the Big bang theory is false .Of all the people who do not believe in postlife,more of them believe in the BigBang theroy .There is statistically a significant difference between believing in postlife versus the Bigbang theory .

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~POSTLIFE + BIGBANG,data=GSS)
rowPerc(table1)
colPerc(table1)
```
About 34% of people who do not believe in postlife believe the bigbang is false and 65 % of people who do not believe in postlife believe that the bigbang is true . Then there is about 56% of people  who do believe in postlife believe that the bigbang is false and 43 % believe that the bigbang is true .

## Inferential Results


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
Let's talk about odds for a second ,of those who believe in postlife ,if you donot believe in postlife what are the oddsof the bigbang  being false ?For those who said no to believing in postlife ,but believe in bigbang ,the odds are 8/15. Now suppose that you do believe in postlife the odds are 88/67.If we had more data,these results would be more significant to make a determination .The odds ratio is 408:1.

```{r}
(8/15)/(88/67)

```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We are forced to say that we fail to reject the null hypothesis because there is not enough data to show .The probability of getting something like this again is .08% of the time which is also the p - value .
